Parameterless Population Pyramid

### 2013-09-20 Parameterless Population Pyramid/main.tex
More references, fixed bottom line in example diagram

\keywords{TODO}

@@

@@

\subsection{Linkage Tree Genetic Algorithm}
TODO Discuss LTGA~\cite{thierens:2013:ltgahiff}, how it differs from P3, its limitation based on
initialization, requirement of population size.  Mention how some
of the ideas in P3 were tried in LTGA and seemed to make improvements~\cite{goldman:2012:ltga}.
Discuss bisection method and Rule of Three~\cite{jovanovic:1997:ruleofthree}.
Remember to say that the paper argues for $\frac{3}{N+1}$, so 100 trails is strictly
less than $3\%$ expected failure rate.

@@

\subsection{Randomly Generated Problem Classes}
TODO Nearest Neighbor NK with wrapping neighborhoods, Ising Spin Glasses on toroidal
grids with only -1, 1 spins~\cite{saul:1994:spinglass}.
Used\footnote{\url{http://www.informatik.uni-koeln.de/spinglass/}}, Maximum Satisfiability constructed with known global
optimum.

>>>>

\keywords{Linkage Learning, Local Search, TODO}

@@

TODO Talk about LO-LIMD~\cite{posik:2011:parameterless} and how it was parameter-less,
but is incapable of handling overlapping linkages.

@@

\subsection{Linkage Tree Genetic Algorithm}
TODO Discuss LTGA~\cite{thierens:2013:ltgahiff}, how it differs from P3, its limitation based on
initialization, requirement of population size.  Mention how some
of the ideas in P3 were tried in LTGA and seemed to make improvements~\cite{goldman:2012:ltga}.
Tests of adding hillclimber to LTGA argued no improvement~\cite{bosman:2011:lsbbo}.
Discuss bisection method and Rule of Three~\cite{jovanovic:1997:ruleofthree}.
Remember to say that the paper argues for $\frac{3}{N+1}$, so 100 trails is strictly
less than $3\%$ expected failure rate.

@@

\subsection{Randomly Generated Problem Classes}
TODO Nearest Neighbor NK with wrapping neighborhoods~\cite{wright:2000:solvingnk}, Ising Spin Glasses on toroidal
grids with only -1, 1 spins~\cite{saul:1994:spinglass}.
Used\footnote{\url{http://www.informatik.uni-koeln.de/spinglass/}}, Maximum Satisfiability constructed with known global
optimum.
